Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/introduction.tex
Minor edits.
Some other minor edit.

Multi-armed bandits (MAB) is a tractable abstraction for the tradeoff between exploration and \emph{exploitation} (making good near-term decisions based on available information). MAB problems have been studied for many decades, see \cite{Bubeck-survey12} for background. We consider a simple and well-understood MAB model with i.i.d. rewards \cite{bandits-ucb1}. We focus on a well-known distinction between the ``greedy" (exploitation-only) algorithm, "naive" MAB  algorithms that separate exploration and exploitation, and better MAB algorithms that combine the two. As a token example of ``near-optimal" bandit algorithms,
we use a classic algorithm called ``Thompson Sampling", see \cite{TS-survey-FTML18} for background.

>>>>

Multi-armed bandits (MAB) is a tractable abstraction for the tradeoff between exploration and \emph{exploitation} (making good near-term decisions based on available information). MAB problems have been studied for many decades, see \cite{Bubeck-survey12} for background. We consider i.i.d. rewards, a well-studied and well-understood MAB model \cite{bandits-ucb1}. We focus on a well-known distinction between ``greedy", exploitation-only algorithms, "naive" algorithms that separate exploration and exploitation, and better algorithms that combine the two.
